Verifying Demonstrations

### 2018-11-30 paper/protocol.tex
Fixes figure ref typos
shortens some titles, integrates protocol overview in text, removes keywords etc. turns paragraphs into subsections for correct numbering

\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\label{Protocol}

@@

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{CLsignAlg}).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{CLacSigAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

The join, participation and submission phases are illustrated in \cref{fig:ProtocolOverview}.
The participation proof share that will be constructed in the participation phase is illustrated in \cref{fig:ProofFig}.

@@

\begin{figure}
  \centering
  \small
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of the Join, Participation and Submission phases of \CROCUS.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
    permanent storage \(S\). Note that \pid always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

>>>>

%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\section{The \CROCUS Protocol}
\label{Protocol}

@@

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

%The join, participation and submission phases are as follows.
% illustrated in \cref{fig:ProtocolOverview}.

The participation proof share that will be constructed in the
participation phase is illustrated in \cref{fig:ProofFig}.

@@

@@

Here is an overview of the protocol.

%\begin{figure}
% \centering
  \small
 % \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
%  \end{minipage}
%  \caption{%
%     An overview of the Join, Participation and Submission phases of \CROCUS.\@
%     The organizer \(O\) broadcasts the manifesto.
%     The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
%     Finally, both \(P\) and \(W\) submit the proof shares to a
%     permanent storage \(S\). Note that \pid always refers to the
%     protester whose presence is being witnessed.
%   }%
%   \label{fig:ProtocolOverview}
% \end{figure}
\normalsize

### 2018-11-30 paper/system-model.tex
shortens some titles, integrates protocol overview in text, removes keywords etc. turns paragraphs into subsections for correct numbering

\section{System model and requirements}%
\label{system-model}

@@

\subsection{System model and physical assumptions}%
\label{assumptions}

@@

We draw inspiration from the three traditionally desired properties for verifiability in voting systems:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal\footnote{%
  Elections also have some temporal aspects, such that one cannot vote at any 
  time and a vote in one election should not be reusable in the next election.
  However, the temporal relation for a protest is not as strictly defined as for 
  elections as a protest can start at any time and last for an arbitrary period 
  of time.%
} and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

>>>>

\section{System model}%
\label{system-model}

@@

\subsection{Assumptions}%
\label{assumptions}

@@

We draw inspiration from the three traditionally desired properties for verifiability in voting systems:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal%\footnote{%
%   Elections also have some temporal aspects, such that one cannot vote at any 
%   time and a vote in one election should not be reusable in the next election.
%   However, the temporal relation for a protest is not as strictly defined as for 
%   elections as a protest can start at any time and last for an arbitrary period 
%   of time.%
% }
and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
